---
title: "rimr: Package for deterministic record linkage"
author: "Michael Škvrňák"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Load data
```{r}
library(magrittr)
library(rimr)

load("../data/kraj_2000.RData")
load("../data/kraj_2004.RData")

kraj_2000$last_name %<>% gsub("l'", "ĺ", .)
kraj_2004$last_name %<>% gsub("l'", "ĺ", .)

kraj_2000$year <- 2000
kraj_2004$year <- 2004

head(kraj_2000)
```

# Find similar
The comparison of records works by taking a row from the source dataset
and looking for record in the target dataset which fulfils conditions
specified by arguments `eq` (equality), `ht`, `lt`, `hte`, `lte`, `eq_tol`,
`eq_sub`.

```{r}

sim1 <- find_similar(source = kraj_2000, 
             target = kraj_2004, 
             row = 1, 
             id = "row_id",
             eq = c("first_name", "last_name", "approx_birth_year", 
                    "residence", "region"), 
             keep_duplicities = FALSE,
             verbose = FALSE)
```

Depending on the conditions, it is possible that there are more than 1 records
fulfilling the conditions. For this reason, you can set the parameter
`keep_duplicities` to FALSE and only the record which shares the most attributes
with the original record will be recorded. You can set the columns used
for finding the most similar using parameter `compare_cols`.  

While the `find_similar` function compares only 1 row, there is a wrapper
function called `find_all_similar` which accepts all parameters passed to
`find_similar` and you can also specify how many `cores` should be used
for computation (using parallel package so applicable only for UNIX).

```{r}
df <- find_all_similar(source = kraj_2000, 
                       target = kraj_2004, 
                       id = "row_id", 
                       eq = c("first_name", "last_name", "approx_birth_year",
                              "residence", "region"), 
                       verbose = FALSE, 
                       cores = 1)
```

The output of the comparison is pivot table which contains
number of rows from source and target dataset for matching 
entities. 

```{r}
head(df)
```

The output contains all of the records from the source dataset
and those records that match with any of the records from the source.
To append the entities from target dataset which do not occur in the 
source dataset use `append_missing` function.

```{r}
out <- append_missing(target = kraj_2004, 
                      target_ids = "row_id", 
                      out = df)
```

Obviously, pivot table is not usually a desired product of comparison. 
Therefore, you can create panel data from the output by calling 
`create_panel_output` which combines source and target datasets
using the output of comparison and adds unique IDs to the entities.

```{r}
panel_data <- create_panel_output(out, id = "person_id")

panel_data %>% dplyr::arrange(person_id) %>% head
```

