---
title: "Sequential matching"
author: "Michael Škvrňák"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r}

library(dplyr)
library(rimr)

load("../data/kraj_2000.RData")
load("../data/kraj_2004.RData")
kraj_2008 <- readr::read_csv("../data/kraj_2008.csv")

kraj_2000$abs_votes <- as.integer(gsub("\\s", "", kraj_2000$abs_votes))
kraj_2004$abs_votes <- as.integer(gsub("\\s", "", kraj_2004$abs_votes))

kraj_2000$last_name <- gsub("l'", "ĺ", kraj_2000$last_name)
kraj_2004$last_name <- gsub("l'", "ĺ", kraj_2004$last_name)

kraj_2004$first_name <- gsub("l'", "ĺ", kraj_2004$first_name)

kraj_2000$year <- 2000
kraj_2004$year <- 2004
kraj_2008$year <- 2008
```

First, find similar between election in 2000 and 2004 and between 2004 and 2008. 
Joining these datasets would omit those candidates who run in 2000 and in 2008 
(but did not run in 2004).
```{r, eval = FALSE}
k_00_04 <- find_all_similar(source = kraj_2000, 
                            target = kraj_2004, 
                            eq = c("first_name", "last_name", "region"), 
                            eq_tol = list(c("approx_birth_year", 1)), 
                            id = "row_id", 
                            keep_duplicities = FALSE, 
                            verbose = TRUE, 
                            cores = 4)

k_04_08 <- find_all_similar(source = kraj_2004, 
                            target = kraj_2008, 
                            eq = c("first_name", "last_name", "region"), 
                            eq_tol = list(c("approx_birth_year", 1)), 
                            id = "row_id", 
                            keep_duplicities = FALSE, 
                            verbose = TRUE, 
                            cores = 4)


```

Thus, we have to find data for those who did not run in 2004 
using `return_missing_data` function.
Also, to make it faster, we should find the data to persons who did run in 2000 but 
not in 2004 using `find_nonconsecutive_data`.

```{r, eval = FALSE}
missing_08 <- find_missing(kraj_2008, "row_id", k_04_08$kraj_2008)
missing_data_08 <- return_missing_data(kraj_2008, "row_id", missing_08)
noncons_04 <- return_nonconsecutive_data(k_00_04, kraj_2000, kraj_2004, "row_id")

```

Then, we compare these two datasets for matching persons.
```{r, eval = FALSE}
k_00_08 <- find_all_similar(noncons_04, missing_data_08, 
                            eq = c("first_name", "last_name", "region"), 
                            eq_tol = list(c("approx_birth_year", 1)), 
                            id = "row_id", 
                            keep_duplicities = FALSE, 
                            verbose = TRUE, 
                            cores = 4)
colnames(k_00_08) <- c("kraj_2000", "kraj_2008")
# panel_00_08 <- create_panel_output(k_00_08)

missing_final_08 <- find_missing(kraj_2008, "row_id", 
                                  c(k_04_08$kraj_2008, k_00_08$kraj_2008))
colnames(missing_final_08) <- c("kraj_2004", "kraj_2008")

k_04_08_2 <- append_missing(target = kraj_2008, 
                            target_ids = "row_id", 
                            out = k_04_08, 
                            found_ids = c(k_04_08$kraj_2008, k_00_08$kraj_2008))
```

```{r, eval = FALSE}
out <- dplyr::full_join(k_00_04, k_04_08, by = c("kraj_2004"))

insert_nonconsecutive <- function(out, noncons_pivot, source, target){
    args <- match.call()
    last_column <- ncol(noncons_pivot)
    running <- noncons_pivot[!is.na(noncons_pivot[, last_column]), ]
    out[out[[as.character(args$source)]] %in% running[[as.character(args$source)]],
        as.character(args$target)] <- running[[as.character(args$target)]]
    out
    
}

out_00_08 <- insert_nonconsecutive(out, k_00_08, kraj_2000, kraj_2008)
out_00_08_with_missing <- dplyr::bind_rows(out_00_08, missing_final_08)
panel_00_08 <- create_panel_output(out_00_08, "person_id")
```

