---
title: "Sequential matching"
author: "Michael Škvrňák"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r}

library(dplyr)
library(rimr)

load("../data/kraj_2000.RData")
load("../data/kraj_2004.RData")
kraj_2008 <- readr::read_csv("../data/kraj_2008.csv")
kraj_2012 <- readr::read_csv("../data/kraj_2012.csv")

kraj_2000$abs_votes <- as.integer(gsub("\\s", "", kraj_2000$abs_votes))
kraj_2004$abs_votes <- as.integer(gsub("\\s", "", kraj_2004$abs_votes))

kraj_2000$last_name <- gsub("l'", "ĺ", kraj_2000$last_name)
kraj_2004$last_name <- gsub("l'", "ĺ", kraj_2004$last_name)

kraj_2004$first_name <- gsub("l'", "ĺ", kraj_2004$first_name)

kraj_2012$mandate <- as.integer(kraj_2012$mandate)

```

First, find similar between election in 2000 and 2004 and between 2004 and 2008. 
Joining these datasets would omit those candidates who run in 2000 and in 2008 
(but did not run in 2004).
```{r, eval = FALSE}
k_00_04 <- find_all_similar(source = kraj_2000, 
                            target = kraj_2004, 
                            eq = c("first_name", "last_name", "region"), 
                            eq_tol = list(c("approx_birth_year", 1)), 
                            id = "row_id", 
                            keep_duplicities = FALSE, 
                            verbose = TRUE, 
                            cores = 4)

k_04_08 <- find_all_similar(source = kraj_2004, 
                            target = kraj_2008, 
                            eq = c("first_name", "last_name", "region"), 
                            eq_tol = list(c("approx_birth_year", 1)), 
                            id = "row_id", 
                            keep_duplicities = FALSE, 
                            verbose = TRUE, 
                            cores = 4)

k_08_12 <- find_all_similar(source = kraj_2008, 
                            target = kraj_2012, 
                            eq = c("first_name", "last_name", "region"), 
                            eq_tol = list(c("approx_birth_year", 1)), 
                            id = "row_id", 
                            keep_duplicities = FALSE, 
                            verbose = TRUE, 
                            cores = 4)


```

Thus, we have to find data for those who did not run in 2004 
using `return_missing_data` function.
Also, to make it faster, we should find the data to persons who did run in 2000 but 
not in 2004 using `find_nonconsecutive_data`.

```{r, eval = FALSE}
missing_08 <- find_missing(kraj_2008, "row_id", k_04_08$kraj_2008)
missing_data_08 <- return_missing_data(kraj_2008, "row_id", missing_08)
noncons_04 <- return_nonconsecutive_data(k_00_04, kraj_2000, kraj_2004, "row_id")

# missing_12 <- find_missing(kraj_2012, "row_id", k_08_12$kraj_2012)
# missing_data_12 <- return_missing_data(kraj_2012, "row_id", missing_12)
# noncons_08 <- return_nonconsecutive_data(k_00_04, kraj_2000, kraj_2004, "row_id")


```

Then, we compare these two datasets for matching persons.
```{r, eval = FALSE}
k_00_08 <- find_all_similar(noncons_04, missing_data_08, 
                            eq = c("first_name", "last_name", "region"), 
                            eq_tol = list(c("approx_birth_year", 1)), 
                            id = "row_id", 
                            keep_duplicities = FALSE, 
                            verbose = TRUE, 
                            cores = 4)
colnames(k_00_08) <- c("kraj_2000", "kraj_2008")
# panel_00_08 <- create_panel_output(k_00_08)

missing_final_08 <- find_missing(kraj_2008, "row_id", 
                                  c(k_04_08$kraj_2008, k_00_08$kraj_2008))
colnames(missing_final_08) <- c("kraj_2004", "kraj_2008")

# k_04_08_2 <- append_missing(target = kraj_2008, 
#                             target_ids = "row_id", 
#                             out = k_04_08, 
#                             found_ids = c(k_04_08$kraj_2008, k_00_08$kraj_2008))

```

```{r, eval = FALSE}
out <- dplyr::full_join(k_00_04, k_04_08, by = c("kraj_2004"))

insert_nonconsecutive <- function(out, noncons_pivot, source, target){
    last_column <- ncol(noncons_pivot)
    running <- noncons_pivot[!is.na(noncons_pivot[, last_column]), ]
    out[out[[source]] %in% running[[source]], target] <- running[[target]]
    out
    
}

out_00_08 <- insert_nonconsecutive(out, k_00_08, "kraj_2000", "kraj_2008")
out_00_08_with_missing <- dplyr::bind_rows(out_00_08, missing_final_08)
panel_00_08 <- create_panel_output(out_00_08, "person_id")

missing_12 <- find_missing(kraj_2012, "row_id", k_08_12$kraj_2012)
missing_data_12 <- return_missing_data(kraj_2012, "row_id", missing_12)
noncons_12 <- return_nonconsecutive_data(k_04_08, kraj_2004, kraj_2008, "row_id")

k_04_12 <- find_all_similar(noncons_12, 
                            missing_data_12, 
                            eq = c("first_name", "last_name", "region"), 
                            eq_tol = list(c("approx_birth_year", 1)), 
                            id = "row_id", 
                            keep_duplicities = FALSE, 
                            verbose = TRUE, 
                            cores = 4)
colnames(k_04_12) <- c("kraj_2004", "kraj_2012")

missing_12_2 <- find_missing(kraj_2012, "row_id", 
                            c(k_08_12$kraj_2012, k_04_12$kraj_2012))
missing_data_12_2 <- return_missing_data(kraj_2012, "row_id", missing_12_2)
noncons_12_2 <- return_nonconsecutive_data(out_00_08_with_missing, 
                                           kraj_2000, kraj_2008, "row_id")

k_00_12 <- find_all_similar(noncons_12_2, 
                            missing_data_12_2, 
                            eq = c("first_name", "last_name", "region"), 
                            eq_tol = list(c("approx_birth_year", 1)), 
                            id = "row_id", 
                            keep_duplicities = FALSE, 
                            verbose = TRUE, 
                            cores = 4)
colnames(k_00_12) <- c("kraj_2000", "kraj_2012")

out_00_12 <- dplyr::full_join(out_00_08_with_missing, k_08_12, by = "kraj_2008")
out_00_12_2 <- insert_nonconsecutive(out_00_12, k_04_12, "kraj_2004", "kraj_2012")
out_00_12_3 <- insert_nonconsecutive(out_00_12_2, k_00_12, "kraj_2000", "kraj_2012")
final_missing <- find_missing(kraj_2012, "row_id", out_00_12_3$kraj_2012)
colnames(final_missing) <- c("kraj_2008", "kraj_2012")

out_00_12_final <- dplyr::bind_rows(out_00_12_3, final_missing)

panel_00_12 <- create_panel_output(out_00_12_final, "person_id", "data")
#noncons_08 <- return_nonconsecutive_data(k_00_04, kraj_2000, kraj_2004, "row_id")
#noncons_00 <- return_nonconsecutive_data(k_00_08, kraj_2000, kraj_2008, "row_id")
```

```{r, eval = FALSE}

rename_output_colnames <- function(out, datasets){
    colnames(out) <- datasets
    out
}


attend_trolley <- function(data, 
                           id, 
                           cores, 
                           compare_cols, 
                           verbose = FALSE, 
                           keep_duplicities, 
                           ...){
    no_datasets <- length(data)
    out <- purrr::map(1:(no_datasets - 1), function(x) 
        find_all_similar(data[[x]], 
                         data[[x + 1]], 
                         id = id, 
                         keep_duplicities = keep_duplicities, 
                         verbose = verbose, 
                         cores = cores, 
                         ...
                         ))
    args <- match.call()
    datasets <- as.character(args$data)
    datasets <- datasets[2:length(datasets)]
    
    out <- purrr::map(1:length(out), function(x) 
        rename_output_colnames(out[[x]], 
                               c(datasets[x], 
                                 datasets[x+1])))
    browser()
    
    missing <- purrr::map(2:length(out), 
                          function(x) 
                              find_missing(target = eval(as.name(datasets[x+1])), 
                                           target_ids = id, 
                                           found_ids = out[[x]][[2]]))
    missing_data <- purrr::map(1:length(missing), function(x) 
        return_missing_data(target = eval(as.name(datasets[2+x])), 
                            row_id = id, 
                            missing = missing[[x]]))
    
    
    
}

out <- attend_trolley(list(kraj_2000, kraj_2004, kraj_2008, kraj_2012), 
                      eq = c("first_name", "last_name", "region"), 
                      eq_tol = list(c("approx_birth_year", 1)), 
                      id = "row_id", 
                      keep_duplicities = FALSE, 
                      verbose = TRUE, 
                      cores = 4)
```

